\documentclass[a4paper,11pt,oneside]{book}
\usepackage{textgreek}
\usepackage{color}
\usepackage{graphicx}
\usepackage{multirow}
\usepackage{sectsty}
\usepackage{unicode-math}
\usepackage[left=1.50in, right=1.00in, top=1.00in, bottom=1.00in]{geometry}
\usepackage{fontspec}
\usepackage{setspace}
\usepackage{lscape}
\usepackage{lmodern}
\usepackage{amsmath}
\usepackage{etoolbox}
\usepackage[normalem]{ulem}
\usepackage[nottoc,notlot,notlof]{tocbibind}

\usepackage{fancyhdr} 
\pagestyle{fancy}
\renewcommand{\sectionmark}[1]{\markright{#1}}
\lhead{}
\rhead{\rightmark}
\cfoot{\thepage}

\usepackage{natbib}
\bibliographystyle{humannat}
\usepackage[hidelinks]{hyperref}
\providecommand*{\backrefsetup}[1]{} % Fix for hyperref crash
\setcounter{secnumdepth}{3}
\unimathsetup{math-style=TeX,mathit=sym,mathbf=sym}
\setmathfont{TeX Gyre Pagella Math}
\setmainfont{TeX Gyre Pagella}
\setsansfont{Berthold Akzidenz Grotesk BE}
%\setsansfont{Comic Sans MS} 				DO NOT USE UNDER ANY CIRCUMSTANCES!
\allsectionsfont{\normalfont\bfseries\sffamily}
%\setcounter{chapter}{-1}

%% Formatting for chapters
\usepackage{titlesec}
\titleformat{\chapter}[display]
{\sffamily \normalsize \huge  \color{black}}%
{\flushright\normalsize \color{black}%
	\MakeUppercase{\chaptertitlename}\hspace{1ex}%
	{\fontsize{60}{60}\selectfont\thechapter}}%
{10 pt}%
{\bfseries\huge}%

% Formatting for captions
\usepackage[figurename=Fig.,labelfont={bf,sf}]{caption}

% Setting appendix
\pretocmd{\chapter}{\renewcommand\thesection{\thechapter.\arabic{section}}}{}{}
\newcommand\appsection{%
	\setcounter{section}{0}%
	\renewcommand\thesection{\thechapter.\Alph{section}}}

\begin{document}
\frontmatter
\include{./TeX_files/title}
\include{./TeX_files/quote}
\tableofcontents

\chapter{Abstract}
The human brain can be divided into multiple areas, each responsible for different aspects of behaviour. For a century we have been developing techniques to non-invasively map these areas and their associated functions, a discipline now known as neuroimaging. In recent years the field has undergone a paradigm shift to investigate how the brain communicates with itself; it is widely regarded that healthy brain function relies upon efficient connectivity between different functional areas, and the neuroimaging field has been revolutionised by our ability to estimate this connectivity. Studies into communication between spatially separate locations in the brain have revealed a series of robust functional networks which govern mental processes. However these studies have been based on the temporal averaging of minutes or even hours of data to give us a generalised 'snapshot' of connectivity. Increasing evidence shows us that these connections are dynamic in space, time and frequency and so the next generation of of neuroimaging methods, which capture this 5-dimensional connectivity will prove to be key tools in the investigation of brain networks and ultimately their breakdown in disease.
\\~\\
In this thesis we introduce novel methods to capture non-stationarity using magnetoencephalography (MEG), an imaging modality which measures the changes in extracranial magnetic fields associated with neuronal current flow. MEG is a direct measurement of neural activity and has an excellent temporal resolution, which makes it  attractive for non-invasively tracking dynamic functional connections. However there are many technical limitations which can confound assessment of functional connectivity which have to be addressed. In Chapters 2 and 3 we introduce the theory behind MEG; specifically how it is possible to measure the femtoTelsa changes in magnetic field generated by the brain and how to project these data to generate a 3-dimensional picture of current in the brain. Chapter 4 reviews some of popular methods of assessing functional connectivity and how to control for the influence of artefactual functional connections erroneously produced during source projection. Chapter 5 introduces a pipeline to assess functional connections across time, space and frequency and in Chapter 6 we apply this pipeline to show that resting state networks, measured using 'static' metrics are in fact comprised of a series of rapidly forming and dissolving subnetwork connections. Finally, Chapter 7 introduces a pipeline to track dynamic network behaviour simultaneously across the entire brain volume and shows that networks can be characterised by their temporal signatures of connectivity.

 \chapter{Acknowledgements}
Without straying too far into the realms of hyperbole, the existence of this thesis would not have been possible without an army of colleagues and friends to keep me advancing. If I could, I would put you all on the front cover, but you'll have to settle for here instead. 
\\~\\
First of all I would like to thank my supervisors, Matt Brookes and Peter Morris, for guiding me along the way these past few years and generally allowing me to flagrantly swing on their coat-tails. I'd also like to thank the collaborators and publication co-authors in Nottingham, Oxford and London; Mark Woolrich, Gareth Barnes, Markus Bauer in particular for lending your weight to make the experimental work what it is. Team MEG members past and present for their input; Siân, Lauren, Prejaas, Ben, Ellie (especially for the interference rejection simulations in Chapter 2), Elena, and last (but not least) Lucrezia for agreeing to proof-read this monster. I would also like to thank the wider Sir Peter Mansfield Imaging Centre community, in particular the residents of The Barn (RIP Downstairs Office), for keeping me entertained and having my back these past few years. Special thanks for Lesley and Liz for dealing with all my ridiculous requests.
\\~\\
On a personal level, I would like to thank my parents Jim and Anna and my brother Billy for the love and support they have given me and letting me be myself. Jenna Flye for brightening my days; even though I'm sure she puts up with me just so she can eventually call herself the Doctor's companion. The friends I made through URN, who let me see into another world I once thought I could never be a part of, and showed how fun masquerading as a 'person in media' could be. In particular I would like to thank Emma Bradshaw for helping me keep it together at the beginning of the PhD when I was almost certain I was going to cave in.  
\\~\\
You are all wonderful human beings and I couldn't have done this without you.
\\~\\
\\~\\
\\~\\
\\~\\
\\~\\
\\~\\
I should also thank the coffee machine. You made tasty beverages and didn't break, and for that I'm grateful. 

\doublespacing

\mainmatter
\include{./TeX_files/introduction}
\include{./TeX_files/chapter01}
\include{./TeX_files/chapter02}
\include{./TeX_files/chapter03}
\include{./TeX_files/chapter04}
\include{./TeX_files/chapter05}
\include{./TeX_files/chapter06}
\include{./TeX_files/conclusions}


\backmatter
\setstretch{1.0}
\bibliography{references}

\end{document}